### 2015-02-27 icfp15-servo/servo.tex
mem mgmt. clarifications from jdm

One area for future improvement is related to allocations that are not owned by Rust itself.
Today, we simple wrap raw C pointers in \lstinline[language=Rust]{unsafe} blocks when we need to use a
custom memory alloctor or interoperate with the SpiderMonkey JavaScript engine from Gecko.
We have implemented wrapper types and compiler plugins that check that these are being used correctly,
but these are still a source of bugs and one of our largest areas of unsafe code.

>>>>

One area for future improvement is related to allocations that are not owned by Rust itself.
Today, we simply wrap raw C pointers in \lstinline[language=Rust]{unsafe} blocks when we need to use a
custom memory alloctor or interoperate with the SpiderMonkey JavaScript engine from Gecko.
We have implemented wrapper types and compiler plugins that restrict incorrect uses of these foreign values,
but these are still a source of bugs and one of our largest areas of unsafe code.
